---
title: "Lab2"
author: "Anna Matarazzo"
date: "9/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Problems

# Problem 1

1. Use R to demonstrate that the mean minimizes the sum of the squared deviations from the mean. Accomplish the following steps:
a. Produce a sample of at least 10 or more different numbers
b. Produce a simulation following the example from the concepts section
c. Use your simulation to test a range of numbers smaller and larger than the mean to show that the mean minimizes the sum of the squared deviations from the mean.
d. Plot your results.

```{r}

scores <- c(4,78,6,8,1,9,7,13,5,3,2)
mean(scores)
scores-mean(scores)
deviations_squared <-(scores-mean(scores))^2
sum(deviations_squared)  

min(scores)
max(scores)
numbers_to_test <- min(scores):max(scores)

sum_deviations_squared <- c()
for(i in numbers_to_test) {
  sum_deviations_squared[i] <- sum((scores-i)^2)
}

sum_deviations_squared

plot(sum_deviations_squared)

```




