---
title: "Lab5"
author: "Anna Matarazzo"
date: "10/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

rnorm(n=10, mean = 0, sd = 1)

library(ggplot2)
some_data <- data.frame(observations = rnorm(n=10000, mean = 0, sd = 1),
                        type = "A")

ggplot(some_data, aes(x=observations)) +
  geom_histogram(bins=100, color="black",
                 fill= 'orange')

some_data$observations[some_data$observations > 2.5]
length(some_data$observations[some_data$observations > 2.5])
length(some_data$observations[some_data$observations > 2.5])/10000


rnorm(n=10, mean = 0, sd = 1)

library(ggplot2)
some_data <- data.frame(density = dnorm(-4:4, mean = 0, sd = 1),
                        x = -4:4)

knitr::kable(some_data)

ggplot(some_data, aes(x=x, y=density)) +
  geom_point()



some_data <- data.frame(density = dnorm(seq(-4,4,.001), mean = 0, sd = 1),
                        x = seq(-4,4,.001))

ggplot(some_data, aes(x=x, y=density)) +
  geom_line()

```


```{r}
library(dplyr)

some_data <- data.frame(density = dnorm(seq(-4,4,.001), mean = 0, sd = 1),
                        x = seq(-4,4,.001))

region_data <- some_data %>%
  filter(x > 2.5)

ggplot(some_data, aes(x=x, y=density)) +
  geom_line()+
  geom_ribbon(data = region_data,
              fill = "red",
              aes(ymin=0,ymax=density))

```

```{r}
pnorm(2.5, mean=0, sd = 1)



```

```{r}
some_data <- data.frame(density = dnorm(seq(-4,4,.001), mean = 0, sd = 1),
                        x = seq(-4,4,.001))
region_data <- some_data %>%
  filter(x < 2.5)

ggplot(some_data, aes(x=x, y=density)) +
  geom_line()+
  geom_ribbon(data = region_data,
              fill = "red",
              aes(ymin=0,ymax=density))


```
```{r}
1 - pnorm(2.5, mean=0, sd = 1)
#> [1] 0.006209665

pnorm(2.5, mean=0, sd = 1, lower.tail=FALSE)
#> [1] 0.006209665

```



```{r}
qnorm(.05, mean= 0, sd =1, lower.tail = FALSE)

```

```{r}
mean(rnorm(10, mean=0, sd =1))


sample_means <- replicate(10000, mean(rnorm(10,0,1)))
hist(sample_means)


sample_means <- replicate(10000, mean(rnorm(10,0,1)))
sd(sample_means)

```

```{r}
sample_means <- replicate(10000, mean(rnorm(10,0,1)))
sd(sample_means)
#> [1] 0.3158243

# analytic SEM

1/sqrt(10)
#> [1] 0.3162278
```



# Problems

## Problem 1

1.Trust but verify. We trust that the rnorm() will generate random deviates in accordance with the definition of the normal distribution. For example, we learned in this lab, that a normal distribution with mean = 0, and sd =1 , should only produce values larger than 2.5 with a specific small probability, that is P(x>2.5) = 0.006209665. Verify this is approximately the case by randomly sampling 1 million numbers from this distribution, and calculate what proportion of numbers are larger than 2.5. (1 point)

```{r}

pnorm(2.5, mean = 0, sd = 1, lower.tail = FALSE)

some_data <- rnorm(n=1000000, mean = 0, sd = 1)

selection <- some_data[some_data > 2.5]
length(selection)/1000000

```

` Confidence level: 02 ` 


## Problem 2

2. If performance on a standardized test was known to follow a normal distribution with mean 100 and standard deviation 10, and 10,000 people took the test, how many people would be expected to achieve a score higher than 3 standard deviations from the mean? (1 point)

# My Verson:

```{r}

some_data <- data.frame(observations = rnorm(n=10000, mean = 100, sd = 10),
                        type = "A")

region_data <- some_data %>%
  filter(some_data$observations > 130)

some_data$observations[some_data$observations > 130]

length(some_data$observations[some_data$observations > 130])

```

` Confidence level: 100 ` 

# Key Verson:
```{r}
pnorm(q = 130, mean = 100, sd = 10, lower.tail = FALSE)

10000*pnorm(q = 130, mean = 100, sd = 10, lower.tail = FALSE)

some_observations <- rnorm(10000,100,10)
length(some_observations[some_observations >130])/10000

```

` Confidence level: 20 `

## Problem 3


















