---
title: "Lab6_v1"
author: "Anna Matarazzo"
date: "10/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---




## Problem 1

1. Write a function that conducts a randomization test for the mean difference between two groups, and show that it works. Specifically, using your function, conduct a randomization test on the same data we used in the above example from lab. Report the results and briefly discuss what the results of the randomization tell you. (6 points). Extra: if the observed mean difference in the experiment was found to be .5, what would you have concluded from the randomization test?

Inputs:
- the inputs should include a vector for group 1, and vector for group 2, and the number of permutations/re-samplings of the data to create.

Outputs:
- output each group mean, and the difference between group means
- output a histogram of the sampling distribution of the possible mean differences produced by the randomization process
- output the probability or odds of obtaining the observed mean difference or larger.

Optional:

- include the ability to calculate the probability of obtaining any mean difference or larger
- deal with negative difference scores appropriately
- add one or two-tailed test options


```{r}
group_one <- c(3,4,5,6,7)
group_two <- c(5,3,2,4,6)

library(dplyr)
  
randomization_test <- function(A, B, resamples = 1000) {
  
  group_A_mean <- mean(A)
  group_B_mean <- mean(B)
  mean_difference <- group_A_mean - group_B_mean
  
 all_means <- c(A,B) 
 
 possible_differences <- c()
 for(i in 1:resamples){
  resample <- sample(all_means)
  new_A_mean <- mean(resample[1:length(A)])
  new_B_mean <- mean(resample[(length(A)+1):length(all_means)])
  possible_differences[i] <- new_A_mean - new_B_mean
  

}
 
 the_plot <- ggplot2::qplot(possible_differences)+
  ggplot2::geom_histogram(color="orange")+
  ggplot2::geom_vline(xintercept=mean_difference, color = "red")+
  ggplot2::theme_classic()

 
# absolute_differences <- abs(possible_differences)
 
  p_value <- length(possible_differences[possible_differences >= mean_difference ] )/resamples
  
  st_dev <- sd(possible_differences)

 
 test_output <- list(A_mean = group_A_mean,
                     B_mean = group_B_mean,
                     difference = mean_difference,
                     randomization = possible_differences,
                     standard_deviation = st_dev,
                     plot = the_plot,
                     p_value = p_value)
 
 return(test_output)
}

randomization_test(A = group_one, 
                   B = group_two, 
                   resamples = 1000)

```







#####





###### Below I tried to find out what is the probability of getting Jenny's number if we randomly sample numbers from 0 to 9, and if we randomly sample only numbers 8675309. I kept it here because I want to finish working on it so that it presents a nice output.

```{r}
a <- sample(x = 0:9, size = 7, replace = FALSE)
samples <- replicate(100000, sample(a))

count_example <- 0
for(i in 1:100000){
  if(sum (samples[,i] == c(8,6,7,5,3,0,9)) == 7) {
    count_example <-  count_example+1
  }
}

count_example
count_example/100000 

```

```{r}
n=100000
samples <- replicate(n, sample(c(0,3,5,6,7,8,9)))

count_example <- 0
for(i in 1:n){
  if(sum (samples[,i] == c(8,6,7,5,3,0,9)) == 7) {
    count_example <-  count_example+1
  }
}

count_example
count_example/n*100

#output <- list (number_of_jennys_numbers = count_example,
                # probability_percent = b)

```


```{r}

factorial(36)






```









