---
title: "Lab7"
author: "Anna Matarazzo"
date: "10/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
binom.test(x=65, n=100, p=0.5, alternative = "greater")
```



```{r}
test_results <- binom.test(x=65, n=100, p=0.5, alternative = "greater")

test_results$p.value

```

Pigeon A was `r test_results$statistic`% correct (p<=`r test_results$p.value`).



```{r}

library(ggplot2)
qplot(y=dbinom(0:100, 100, .5))+
  geom_bar(stat='identity', position="dodge")+
  ylab('density')+
  xlab('#of successes')

sum(dbinom(0:100, 100, .5))

sum(dbinom(65:100, 100, .5))



```



```{r}
binom.test(x=7, n=10, alternative = "greater")

```


```{r}
coin_flips <- data.frame (number_of_heads = 0:10,
                          probability = dbinom(x=0:10, size=10, prob=.5),
                          cumulative=pbinom(0:10, size=10,prob=.5),
                          rev_cumulative = pbinom(-1:9,10,.5, lower.tail = FALSE))

knitr::kable(coin_flips)

```


```{r}
task_designs <- data.frame (number_of_heads = 0:1,
                          probability = dbinom(x=0:1, size=1, prob=.5),
                          cumulative=pbinom(0:1, size=1,prob=.5),
                          rev_cumulative = pbinom(-1:0,1,.5, lower.tail = FALSE))

knitr::kable(task_designs)

```


```{r}
task_designs <- data.frame (number_of_heads = 0:2,
                          probability = dbinom(x=0:2, size=2, prob=.5),
                          cumulative=pbinom(0:2, size=2,prob=.5),
                          rev_cumulative = pbinom(-1:1,1,.5, lower.tail = FALSE))

knitr::kable(task_designs)

```

```{r}
task_designs <- data.frame (number_of_heads = 0:2,
                          probability = dbinom(x=0:2, size=2, prob=.5),
                          cumulative=pbinom(0:2, size=2,prob=.5),
                          rev_cumulative = pbinom(-1:1,1,.5, lower.tail = FALSE))

knitr::kable(task_designs)

```

```{r}
task_designs <- data.frame (number_of_heads = 0:3,
                          probability = dbinom(x=0:3, size=3, prob=.5),
                          cumulative=pbinom(0:3, size=3,prob=.5),
                          rev_cumulative = pbinom(-1:2,3,.5, lower.tail = FALSE))

knitr::kable(task_designs)

```

```{r}
binom.test(x=51, n=100, .5, alternative = "greater")

```

```{r}
binom.test(x=5100, n=10000, .5, alternative = "greater")

```


## Problem 1

1. A test-taker answered 50 true/false questions and received a score of 60% correct. Report the results of a binomial test and explain whether you think the test-score could be produced by the test-taker randomly guessing on each question. (2 points)


```{r}

binom_test1 <- binom.test(x=50*0.6, n=50, .5, alternative = "greater")

binom_test1 


p_value <- format(round(binom_test1$p.value, 4), nsmall = 2)
p_value_percent <- format(round(binom_test1$p.value*100, 2), nsmall = 2)

library(ggplot2)
qplot(y=dbinom(0:50, 50, .5))+
  geom_bar(stat='identity', position="dodge")+
  ylab('density')+
  xlab('#of successes')

```

A test-taker answered `r binom_test1$statistic` questions correctly with a p value <=`r p_value`. Which means there is a `r p_value_percent`% chance that she would get the same result if she guessed the answers. This result is not statistically significant if we take the commonly accepted level of significance of p=0.05, which means that the result was unlikely to happen due to chance. Still I would not bet my collection of old payphone cards on that she didn't guess the answers because `r p_value` is still a good chance.





























































