---
title: "Lab9"
author: "Anna Matarazzo"
date: "11/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

my_vals <- c(20,30, 10, 10, 30, 30)
(xsq <- chisq.test(my_vals))

xsq$statistic
xsq$observed
xsq$expected
xsq$residuals

b <- c((xsq$observed-xsq$expected)/sqrt(xsq$expected))
b

z <- c(((xsq$observed - xsq$expected)^2) / xsq$expected)
z

sum(((xsq$observed - xsq$expected)^2) / xsq$expected)

```


```{r}

M <- as.table(rbind(c(762,327,468), c(484,239,477)))
dimnames(M) <- list(gender = c("F","M"),
                    party = c("Democrat", "Independent", "Republican"))
(Xsq <- chisq.test(M))
Xsq$observed
Xsq$expected
Xsq$residuals
Xsq$stdres

```



```{r}
coin_toss <- data.frame(outcome = c("H", "T"),
                        O = c(23,27),
                        E = c(25,25))
knitr::kable(coin_toss)

library(dplyr)

coin_toss <- coin_toss %>%
  mutate(d = O-E) %>%
  mutate(d_sq = d^2) %>%
  mutate(div = d_sq/E)

knitr::kable(coin_toss)

sum(coin_toss$div)

   O <- c(23,27)
   E <- c(25,25)
   sum((O-E)^2/E)
   
chisq.test(x=c(23,27))
   

```


```{r}

my_vals <- c(47, 3)
chisq.test(my_vals)

```

```{r}

hist(rnorm(10000, 0, 1), breaks = 100)

```


```{r}

hist(rnorm(10000, 0, 1)^2, breaks = 100)

```

```{r}

hist(rchisq(10000, 1), breaks = 100)

```



```{r}

# k=1
from_normal <- replicate(10000, rnorm(1,0,1)^2)
from_chisq <- rchisq(10000,1)
plot_df <- data.frame(values = c(from_normal,
                                 from_chisq),
                      source = c("normal^2", "chisq"))

library(ggplot2)
ggplot(plot_df, aes(x=values))+
  geom_histogram(bins=100)+
  ggtitle("k=1")+
  facet_wrap(~source)

```



```{r}

# k=2
from_normal <- replicate(10000, sum(rnorm(2,0,1)^2))
from_chisq <- rchisq(10000,2)
plot_df <- data.frame(values = c(from_normal,
                                 from_chisq),
                      source = c("normal^2", "chisq"))

library(ggplot2)
ggplot(plot_df, aes(x=values))+
  geom_histogram(bins=100)+
  ggtitle("k=1")+
  facet_wrap(~source)

```

```{r}

# k=3
from_normal <- replicate(10000, sum(rnorm(3,0,1)^2))
from_chisq <- rchisq(10000,3)
plot_df <- data.frame(values = c(from_normal,
                                 from_chisq),
                      source = c("normal^2", "chisq"))

library(ggplot2)
ggplot(plot_df, aes(x=values))+
  geom_histogram(bins=100)+
  ggtitle("k=1")+
  facet_wrap(~source)

```


```{r}

# k=5
from_normal <- replicate(10000, sum(rnorm(5,0,1)^2))
from_chisq <- rchisq(10000,5)
plot_df <- data.frame(values = c(from_normal,
                                 from_chisq),
                      source = c("normal^2", "chisq"))

library(ggplot2)
ggplot(plot_df, aes(x=values))+
  geom_histogram(bins=100)+
  ggtitle("k=1")+
  facet_wrap(~source)

```


```{r}

plot_df <- data.frame(values = c(dchisq(x=seq(0,20,length.out = 100), df=1),
                                 dchisq(x=seq(0,20,length.out = 100), df=3),
                                 dchisq(x=seq(0,20,length.out = 100), df=5),
                                 dchisq(x=seq(0,20,length.out = 100), df=9),
                                 dchisq(x=seq(0,20,length.out = 100), df=11)
                                 ),
                      x = rep(seq(0,20,length.out = 100),5),
                      k = as.factor(rep(c(1,3,5,9,11), each = 100))
)

ggplot(plot_df, aes(x=x, y=values, color=k, group=k))+
  geom_line()+
  ylab("density")+
  xlab("chi-squared")+
  scale_x_continuous(breaks=0:20)




```



```{r}

a <- replicate(10000, sum(rnorm(5, 0, 1)^2))
hist(a)

```


```{r}
mean(rnorm(10000, 0, 1))
```


```{r}
mean(rnorm(10000, 0, 1)^2)
```

```{r}
mean(rchisq(10000, 5))
```


```{r}
hist(rbinom(10000, 10,.5), breaks = seq(0,10,1))
```

```{r}
hist(rbinom(10000, 100,.5), breaks = seq(20,80,1))
```




```{r}

pbinom(2, 10,.5, lower.tail=TRUE)*2

```

```{r}

chisq.test(c(2, 8))

```



```{r}

pbinom(40, 100,.5, lower.tail=TRUE)*2

chisq.test(c(40, 60))

```

```{r}

pbinom(450, 1000,.5, lower.tail=TRUE)*2

chisq.test(c(450, 550))

```

```{r}

pbinom(4500, 10000,.5, lower.tail=TRUE)*2

chisq.test(c(4500, 5500))

```


### Problems

## Problem 1

1. The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).

```{r}

the_data <- read.csv(file="Lab9/Infant_Data.csv")

library(dplyr)

e1_data <- the_data %>%
  filter(ExperimentNumber == "1")

sum_C <- sum(e1_data$Infant.Chose.C)
total_C <- length(e1_data$Infant.Chose.C)

(binomial_p <- pbinom(q=total_C - sum_C,
                      size=total_C, 
                      prob = 0.5,
                      lower.tail=TRUE)*2)

library(tidyr)

gender_choice_table <- e1_data %>%
  group_by(Gender, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(Gender),
              values_from = counts)

gender_choice_table <- gender_choice_table[,2:3]

(gender_Xsq <- chisq.test(gender_choice_table))

uncorrected_Xsq <-
  sum((gender_Xsq$observed - gender_Xsq$expected)^2/gender_Xsq$expected)

gender_Xsq_unc <- pchisq(uncorrected_Xsq, 1, lower.tail = FALSE)

age_table <- e1_data %>%
  group_by(AgeMonths, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(AgeMonths),
              values_from = counts)

age_table[is.na(age_table)] <- 0
age_table <- as.matrix(age_table[,2:21])
(age_xs <- chisq.test(age_table))

age_xs$observed
age_xs$expected

```


` Confidence level - 10. ` 


## Original text from the authors results

However, in the critical test trial that followed, 16 of 21 infants (76.2%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = .026, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$ (19, N=21)=18.24,p=.506,and $\chi^2$ (1,N=21)=0.15,p= .696, respectively.


## Reproductible report using above re-analysis

However, in the critical test trial that followed, `r sum_C` of `r total_C` infants ( `r sum_C/total_C` %) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = `r round(binomial_p, digits=3)`, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$ (`r age_xs$parameter`, N=`r sum(age_xs$observed)`)=`r round(age_xs$statistic, digits=3)` , p=`r round(age_xs$p.value, digits=3)`,and $\chi^2$ (1,N=21)=`r round(uncorrected_Xsq, digits=3)`,p=`r round(gender_Xsq_unc, digits=3)`, respectively.


















