---
title: "Lab9"
author: "Anna Matarazzo"
date: "11/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Problems

## Problem 1

1. The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).

```{r}

the_data <- read.csv(file="Lab9/Infant_Data.csv")

library(dplyr)

e1_data <- the_data %>%
  filter(ExperimentNumber == "1")

sum_C <- sum(e1_data$Infant.Chose.C)
total_C <- length(e1_data$Infant.Chose.C)

(binomial_p <- pbinom(q=total_C - sum_C,
                      size=total_C, 
                      prob = 0.5,
                      lower.tail=TRUE)*2)

library(tidyr)

gender_choice_table <- e1_data %>%
  group_by(Gender, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(Gender),
              values_from = counts)

gender_choice_table <- gender_choice_table[,2:3]

(gender_Xsq <- chisq.test(gender_choice_table))

uncorrected_Xsq <-
  sum((gender_Xsq$observed - gender_Xsq$expected)^2/gender_Xsq$expected)

gender_Xsq_unc <- pchisq(uncorrected_Xsq, 1, lower.tail = FALSE)

age_table <- e1_data %>%
  group_by(AgeMonths, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(AgeMonths),
              values_from = counts)

age_table[is.na(age_table)] <- 0
age_table <- as.matrix(age_table[,2:21])
(age_xs <- chisq.test(age_table))

age_xs$observed
age_xs$expected

```


` Confidence level - 10. ` 


## Original text from the authors results

However, in the critical test trial that followed, 16 of 21 infants (76.2%) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = .026, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$ (19, N=21)=18.24,p=.506,and $\chi^2$ (1,N=21)=0.15,p= .696, respectively.


## Reproductible report using above re-analysis

However, in the critical test trial that followed, `r sum_C` of `r total_C` infants ( `r sum_C/total_C` %) chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = `r round(binomial_p, digits=3)`, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$ (`r age_xs$parameter`, N=`r sum(age_xs$observed)`)=`r round(age_xs$statistic, digits=3)` , p=`r round(age_xs$p.value, digits=3)`,and $\chi^2$ (1,N=21)=`r round(uncorrected_Xsq, digits=3)`,p=`r round(gender_Xsq_unc, digits=3)`, respectively.


















